Usenet Project - CSV Cleaning

### 2024-09-01 Scripts - Data Cleaning and Visuals/Paper Visualizations.Rmd
testing

---
title: "Web Page Visualization Code"
author: "Emerson Johnston"
lastmodifeddate: "2024-08-24"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

@@

# Load the datasets
all_threads <- read.csv(file.path(threads_directory, "aids_related_threads.csv"))
all_comments <- read.csv(file.path(comments_directory, "aids_related_comments.csv"))
```

```{r R CSV Cleaning}
all_threads <- all_threads %>% drop_na()
all_comments <- all_comments %>% drop_na()

# Ensure the 'Date' columns are properly formatted as Date objects
all_comments$Date <- as.Date(all_comments$Date, format = "%Y-%m-%d")
all_threads$Date <- as.Date(all_threads$Date, format = "%Y-%m-%d")

# Filter the datasets to include only data before January 1, 1989
all_comments <- all_comments %>%
  filter(Date < as.Date("1989-01-01")) %>% filter(Date > as.Date("1982-01-01"))

all_threads <- all_threads %>%
  filter(Date < as.Date("1989-01-01")) %>% filter(Date > as.Date("1982-01-01"))

write.csv(all_threads, file.path(threads_directory, "threads_cleaned_82TO89.csv"), row.names = FALSE)
write.csv(all_comments, file.path(comments_directory, "comments_cleaned_82TO89.csv"), row.names = FALSE)
```

@@

# Load the datasets with the correct file paths
all_threads = pd.read_csv(os.path.join(threads_directory, "threads_cleaned_82TO89.csv"))
all_comments = pd.read_csv(os.path.join(comments_directory, "comments_cleaned_82TO89.csv"))
```

# Initial Visualizations - Python
```{python Distribution of Comments per Newsgroup}
plt.figure(figsize=(10, 6))
sns.countplot(data=all_comments, x='newsgroup', order=all_comments['newsgroup'].value_counts().index)
plt.title('Distribution of Comments per Newsgroup')
plt.xticks(rotation=45)
plt.tight_layout()
plt.savefig(os.path.join(output_directory, "images and tables/distribution_of_comments_per_newsgroup.png"))
plt.show()
```

```{python Number of Threads Over Time}
all_threads['Date'] = pd.to_datetime(all_threads['Date'])

plt.figure(figsize=(10, 6))
all_threads.groupby(all_threads['Date'].dt.to_period('M')).size().plot(kind='line')
plt.title('Number of Threads Across All Newsgroups Over Time')
plt.xlabel('Month')
plt.ylabel('Number of Threads')
plt.tight_layout()
plt.savefig(os.path.join(output_directory, "images and tables/number_of_threads_over_time.png"))
plt.show()
```

```{python Average Number of Comments per Thread by Newsgroup}
avg_comments_per_thread = all_threads.groupby('newsgroup')['Number.of.Messages'].mean().reset_index()

plt.figure(figsize=(10, 6))
sns.barplot(data=avg_comments_per_thread, x='newsgroup', y='Number.of.Messages', order=avg_comments_per_thread.sort_values('Number.of.Messages', ascending=False)['newsgroup'])
plt.title('Average Number of Comments per Thread by Newsgroup')
plt.xlabel('Newsgroup')
plt.ylabel('Average Number of Comments')
plt.xticks(rotation=45)
plt.tight_layout()
plt.savefig(os.path.join(output_directory, "images and tables/average_comments_per_thread_by_newsgroup.png"))
plt.show()
```

```{python Sentiment Score Distribution Across All Comments}
plt.figure(figsize=(10, 6))
sns.histplot(all_comments['SentimentScore'], bins=30, kde=True)
plt.title('Sentiment Score Distribution Across All Comments')
plt.xlabel('Sentiment Score')
plt.ylabel('Frequency')
plt.tight_layout()
plt.savefig(os.path.join(output_directory, "images and tables/sentiment_score_distribution_across_all_comments.png"))
plt.show()
```

```{python Top 25 Most Active Users}
import pandas as pd
import matplotlib.pyplot as plt
import seaborn as sns

# Get the top 25 authors by the number of comments
top_authors = all_comments['Author'].value_counts().head(25).index

# Filter the dataset to include only the top 25 authors
top_authors_data = all_comments[all_comments['Author'].isin(top_authors)]

# Calculate the number of comments by each of the top 25 authors in each newsgroup
comments_per_newsgroup = top_authors_data.groupby(['Author', 'newsgroup']).size().unstack(fill_value=0)

# Sort authors by total number of comments in descending order
comments_per_newsgroup['Total Comments'] = comments_per_newsgroup.sum(axis=1)
comments_per_newsgroup = comments_per_newsgroup.sort_values('Total Comments', ascending=True)

# Remove the 'Total Comments' column for plotting
comments_per_newsgroup = comments_per_newsgroup.drop(columns='Total Comments')

# Define a distinct color palette for newsgroups
distinct_colors = sns.color_palette('tab20', len(comments_per_newsgroup.columns))

# Plot a stacked bar plot without white lines between colors and with distinct colors
comments_per_newsgroup.plot(kind='barh', stacked=True, figsize=(12, 8), color=distinct_colors, edgecolor='none')

plt.title('Top 25 Most Active Users by Newsgroup')
plt.xlabel('Number of Comments')
plt.ylabel('Author')
plt.legend(title='Newsgroup', bbox_to_anchor=(1.05, 1), loc='upper left')
plt.tight_layout()

# Save the figure
plt.savefig(os.path.join(output_directory, "images and tables/top_25_most_active_users_by_newsgroup.png"))
plt.show()
```

```{python Temporal Heatmap of Daily Activity by Newsgroup}
import pandas as pd
import matplotlib.pyplot as plt
import seaborn as sns

# Convert 'Date.and.Time' to datetime and handle errors
all_comments['Date.and.Time'] = pd.to_datetime(all_comments['Date.and.Time'], errors='coerce')

# Check if there are any conversion issues and drop those rows
all_comments = all_comments.dropna(subset=['Date.and.Time'])

# Extract day of the week and hour
all_comments['DayOfWeek'] = all_comments['Date.and.Time'].dt.day_name()
all_comments['Hour'] = all_comments['Date.and.Time'].dt.hour

# Group data by DayOfWeek and Hour for all newsgroups combined
activity_data = all_comments.groupby(['DayOfWeek', 'Hour']).size().reset_index(name='Activity')

# Pivot table to prepare data for heatmap
heatmap_data = activity_data.pivot_table(index='Hour', columns='DayOfWeek', values='Activity', fill_value=0)

# Reorder days of the week for consistent display
day_order = ['Monday', 'Tuesday', 'Wednesday', 'Thursday', 'Friday', 'Saturday', 'Sunday']
heatmap_data = heatmap_data[day_order]

# Create the heatmap
plt.figure(figsize=(12, 8))
sns.heatmap(heatmap_data, cmap='viridis')
plt.title('Daily Activity Heatmap Across All Newsgroups')
plt.xlabel('Day of Week')
plt.ylabel('Hour of Day')
plt.tight_layout()
plt.savefig(os.path.join(output_directory, "images and tables/combined_daily_activity_heatmap.png"))
plt.show()
```

```{python Word Clouds!}
import pandas as pd
from wordcloud import WordCloud
import matplotlib.pyplot as plt
from nltk.corpus import stopwords
import nltk
import os

# Ensure NLTK stopwords are downloaded
nltk.download('stopwords')
stop_words = set(stopwords.words('english'))

# Combine all text data into one string for all comments
all_text = " ".join(all_comments['Full.Text'].dropna())

# Create word cloud for all comments
wordcloud_all = WordCloud(width=800, height=400, background_color='white', stopwords=stop_words, collocations=False).generate(all_text)

plt.figure(figsize=(10, 6))
plt.imshow(wordcloud_all, interpolation='bilinear')
plt.axis('off')
plt.title('Most Common Words in All Usenet Comments')
plt.tight_layout()
plt.savefig(os.path.join(output_directory, "images and tables/word_cloud_all_comments.png"))
plt.show()

# Generate word clouds by newsgroup
for newsgroup in all_comments['newsgroup'].unique():
    # Filter comments for the current newsgroup
    group_text = " ".join(all_comments[all_comments['newsgroup'] == newsgroup]['Full.Text'].dropna())

    # Create word cloud for the specific newsgroup
    wordcloud_group = WordCloud(width=800, height=400, background_color='white', stopwords=stop_words, collocations=False).generate(group_text)

    plt.figure(figsize=(10, 6))
    plt.imshow(wordcloud_group, interpolation='bilinear')
    plt.axis('off')
    plt.title(f'Most common words in {newsgroup}')
    plt.tight_layout()

    # Use f-string to save the file with the specific newsgroup name
    plt.savefig(os.path.join(output_directory, f"images and tables/word_cloud_{newsgroup}.png"))
    plt.show()
```

```{python Growth of Newsgroups Over Time}
# Convert Date to datetime format
all_threads['Date'] = pd.to_datetime(all_threads['Date'])

# Calculate cumulative count of newsgroups created over time
plt.figure(figsize=(10, 6))
all_threads.groupby(all_threads['Date'].dt.to_period('M')).newsgroup.nunique().cumsum().plot(kind='line')
plt.title('Growth of Newsgroups Over Time')
plt.xlabel('Month')
plt.ylabel('Cumulative Number of Newsgroups')
plt.tight_layout()
plt.savefig(os.path.join(output_directory, "images and tables/growth_of_newsgroups_over_time.png"))
plt.show()
```

```{python Author Engagement Scatter Plot}
# Calculate number of comments and threads per author
author_stats = all_comments.groupby('Author').agg({'Thread.ID': pd.Series.nunique, 'Unique_CommentID': 'count'}).reset_index()
author_stats.columns = ['Author', 'Threads_Initiated', 'Comments_Made']

plt.figure(figsize=(10, 6))
sns.scatterplot(data=author_stats, x='Threads_Initiated', y='Comments_Made', alpha=0.6)
plt.title('Author Engagement: Comments Made vs. Threads Initiated')
plt.xlabel('Number of Threads Initiated')
plt.ylabel('Number of Comments Made')
plt.tight_layout()
plt.savefig(os.path.join(output_directory, "images and tables/author_engagement_scatterplot.png"))
plt.show()
```

# Sentiment Visualizations - Python
```{python Average Sentiment Over Time Across All Newsgroups}
import pandas as pd
import matplotlib.pyplot as plt

# Ensure 'Date' is in datetime format
all_comments['Date'] = pd.to_datetime(all_comments['Date'])

# Group by month and calculate average sentiment
sentiment_over_time = all_comments.groupby(all_comments['Date'].dt.to_period('M'))['SentimentScore'].mean().reset_index()
sentiment_over_time['Date'] = sentiment_over_time['Date'].dt.to_timestamp()

plt.figure(figsize=(12, 6))
plt.plot(sentiment_over_time['Date'], sentiment_over_time['SentimentScore'], marker='o', linestyle='-')
plt.title('Average Sentiment Over Time Across All Newsgroups')
plt.xlabel('Date')
plt.ylabel('Average Sentiment Score')
plt.xticks(rotation=45)
plt.tight_layout()
plt.savefig(os.path.join(output_directory, "images and tables/sentiment_over_time.png"))
plt.show()
```

```{python Sentiment Distribution by Newsgroup Boxplot}
import seaborn as sns

plt.figure(figsize=(12, 6))
sns.boxplot(x='newsgroup', y='SentimentScore', data=all_comments)
plt.title('Sentiment Distribution by Newsgroup')
plt.xlabel('Newsgroup')
plt.ylabel('Sentiment Score')
plt.xticks(rotation=45)
plt.tight_layout()
plt.savefig(os.path.join(output_directory, "images and tables/sentiment_distribution_by_newsgroup.png"))
plt.show()
```

```{python Monthly Sentiment Heatmap by Newsgroup}
# Group by newsgroup and month to calculate average sentiment
monthly_sentiment = all_comments.groupby([all_comments['Date'].dt.to_period('M'), 'newsgroup'])['SentimentScore'].mean().reset_index()
monthly_sentiment['Date'] = monthly_sentiment['Date'].dt.to_timestamp()

# Pivot table for heatmap
heatmap_data = monthly_sentiment.pivot('newsgroup', 'Date', 'SentimentScore')

plt.figure(figsize=(12, 8))
sns.heatmap(heatmap_data, cmap='coolwarm', center=0)
plt.title('Monthly Sentiment Heatmap by Newsgroup')
plt.xlabel('Month')
plt.ylabel('Newsgroup')
plt.xticks(rotation=45)
plt.tight_layout()
plt.savefig(os.path.join(output_directory, "images and tables/monthly_sentiment_heatmap.png"))
plt.show()
```

```{python Sentiment Score Over Time by Newsgroup}
import pandas as pd
import matplotlib.pyplot as plt
import seaborn as sns

# Ensure 'Date' is in datetime format
all_comments['Date'] = pd.to_datetime(all_comments['Date'])

# Group by month and newsgroup to calculate average sentiment
sentiment_by_newsgroup = all_comments.groupby([all_comments['Date'].dt.to_period('M'), 'newsgroup'])['SentimentScore'].mean().reset_index()
sentiment_by_newsgroup['Date'] = sentiment_by_newsgroup['Date'].dt.to_timestamp()

plt.figure(figsize=(14, 8))
sns.lineplot(data=sentiment_by_newsgroup, x='Date', y='SentimentScore', hue='newsgroup', marker='o')
plt.title('Average Sentiment Over Time by Newsgroup')
plt.xlabel('Date')
plt.ylabel('Average Sentiment Score')
plt.xticks(rotation=45)
plt.tight_layout()
plt.savefig(os.path.join(output_directory, "images and tables/sentiment_over_time_by_newsgroup.png"))
plt.show()
```

```{python Sentiment Polarity Distribution (Positive vs. Negative)}
# Define positive and negative sentiment based on threshold
positive_threshold = 0
all_comments['SentimentPolarity'] = all_comments['SentimentScore'].apply(lambda x: 'Positive' if x > positive_threshold else 'Negative')

plt.figure(figsize=(8, 6))
sns.countplot(data=all_comments, x='SentimentPolarity', palette=['red', 'green'])
plt.title('Sentiment Polarity Distribution')
plt.xlabel('Sentiment Polarity')
plt.ylabel('Number of Comments')
plt.tight_layout()
plt.savefig(os.path.join(output_directory, "images and tables/sentiment_polarity_distribution.png"))
plt.show()
```

```{python Sentiment Trend Analysis with Rolling Average}
# Calculate rolling average of sentiment over time
all_comments['RollingSentiment'] = all_comments['SentimentScore'].rolling(window=30, min_periods=1).mean()

plt.figure(figsize=(12, 6))
plt.plot(all_comments['Date'], all_comments['RollingSentiment'], color='purple')
plt.title('Sentiment Trend Analysis with Rolling Average')
plt.xlabel('Date')
plt.ylabel('Rolling Average Sentiment Score (30-day window)')
plt.xticks(rotation=45)
plt.tight_layout()
plt.savefig(os.path.join(output_directory, "images and tables/sentiment_trend_rolling_average.png"))
plt.show()
```

```{python Top Words Associated with Positive and Negative Sentiments}
from wordcloud import WordCloud

# Separate positive and negative comments
positive_comments = " ".join(all_comments[all_comments['SentimentPolarity'] == 'Positive']['Full.Text'].dropna())
negative_comments = " ".join(all_comments[all_comments['SentimentPolarity'] == 'Negative']['Full.Text'].dropna())

# Create word cloud for positive sentiment
wordcloud_positive = WordCloud(width=800, height=400, background_color='white', stopwords=stop_words, collocations=False).generate(positive_comments)

plt.figure(figsize=(10, 6))
plt.imshow(wordcloud_positive, interpolation='bilinear')
plt.axis('off')
plt.title('Top Words in Positive Sentiment Comments')
plt.tight_layout()
plt.savefig(os.path.join(output_directory, "images and tables/word_cloud_positive_sentiment.png"))
plt.savefig(0_output_path)
plt.show()

# Create word cloud for negative sentiment
wordcloud_negative = WordCloud(width=800, height=400, background_color='white', stopwords=stop_words, collocations=False).generate(negative_comments)

plt.figure(figsize=(10, 6))
plt.imshow(wordcloud_negative, interpolation='bilinear')
plt.axis('off')
plt.title('Top Words in Negative Sentiment Comments')
plt.tight_layout()
plt.savefig(os.path.join(output_directory, "images and tables/word_cloud_negative_sentiment.png"))
plt.show()
```

# Network Visualizations - R
```{r Get Authors Metadata}
# Step 1: Calculate basic metadata for each author
metadata <- all_comments %>%
  group_by(Author) %>%
  summarize(
    total_threads = n_distinct(Thread.ID),  # Count distinct threads per author
    total_comments = n(),  # Total number of comments made by the author
    threads_started = sum(Thread_Relative_CommentID == "CM00001", na.rm = TRUE),  # Number of threads started by the author
    .groups = 'drop'
  )

# Step 2: Calculate comments per newsgroup for each author
comments_per_newsgroup <- all_comments %>%
  group_by(Author, newsgroup) %>%
  summarize(total_comments_in_newsgroup = n(), .groups = 'drop')

# Step 3: Pivot the newsgroup data to wide format to create separate columns for each newsgroup
comments_per_newsgroup_wide <- comments_per_newsgroup %>%
  pivot_wider(
    names_from = newsgroup,
    values_from = total_comments_in_newsgroup,
    values_fill = list(total_comments_in_newsgroup = 0)  # Fill missing values with 0
  )

# Step 4: Merge the metadata with the wide format newsgroup data
metadata <- metadata %>%
  left_join(comments_per_newsgroup_wide, by = "Author")

# Step 5: Calculate author influence based on the number of connections in the network
# Calculate the degree (number of connections) for each author in the graph
edges <- all_comments %>%
  filter(Thread.ID != "") %>%
  group_by(Thread.ID) %>%
  filter(n() > 1) %>%
  summarize(edgelist = list(combn(Author, 2, simplify = FALSE))) %>%
  unnest(edgelist) %>%
  unnest_wider(edgelist, names_sep = "") %>%
  rename(source = edgelist1, target = edgelist2) %>%
  filter(source != target) %>%
  group_by(source, target) %>%
  summarize(weight = n(), .groups = 'drop')

# Create graph object
graph <- igraph::graph_from_data_frame(edges, directed = FALSE)

# Calculate the degree for each author as their influence
author_influence <- data.frame(
  Author = igraph::V(graph)$name,
  influence = igraph::degree(graph)
)

# Step 6: Merge author influence into metadata
metadata <- metadata %>%
  left_join(author_influence, by = "Author")

# Step 7: Perform community detection using Louvain algorithm
communities <- cluster_louvain(graph)
membership <- membership(communities)

# Step 8: Create node_communities DataFrame
node_communities <- data.frame(
  name = V(graph)$name,  # Node names (authors)
  community = membership  # Community assignment
)

# Step 9: Sort the metadata DataFrame by total_comments in descending order
metadata <- metadata %>%
  arrange(desc(total_comments))

# Preview the updated metadata dataframe
print(metadata)
print(node_communities)  # Display node communities
```

```{r Create Edges and Nodes}
# Create top_authors list for the top 15 authors by influence
top_authors <- metadata %>%
  arrange(desc(influence)) %>%
  slice(1:20) %>%
  pull(Author)

# Filter metadata and comments data for only top authors
metadata <- metadata %>%
  filter(Author %in% top_authors)

comments_per_newsgroup_wide <- comments_per_newsgroup_wide %>%
  filter(Author %in% top_authors)

# Step 10: Create Edges and Nodes for the visualization

# Filter edges to include only those involving top authors
edges <- edges %>%
  filter(source %in% top_authors & target %in% top_authors)

# Prepare nodes data
nodes <- data.frame(
  name = top_authors,
  size = author_influence$influence[match(top_authors, author_influence$Author)],
  label = top_authors
)

# Merge nodes with their community data
nodes <- nodes %>%
  left_join(node_communities, by = "name")

# Add metadata and newsgroup comments in descending order to the title
nodes <- nodes %>%
  mutate(
    # Calculate the newsgroup comments section dynamically
    comments_per_newsgroup = sapply(name, function(author_name) {
      author_data <- comments_per_newsgroup_wide %>%
        filter(Author == author_name) %>%
        select(-Author) %>%
        pivot_longer(cols = everything(), names_to = "newsgroup", values_to = "comments") %>%
        arrange(desc(comments))

      paste(author_data$newsgroup, author_data$comments, sep = ": ", collapse = "<br>")
    }),

    # Prepare the title with the formatted metadata and comments per newsgroup
    title = paste0(
      "<div style='background-color: #f2f2f2; border: 2px solid #666666; padding: 5px;'>",  # Custom tooltip styling
      "<strong>", name, "</strong><br>",
      "Total Threads Participated: ", metadata$total_threads[match(name, metadata$Author)], "<br>",
      "Total Comments: ", metadata$total_comments[match(name, metadata$Author)], "<br>",
      "Threads Started: ", metadata$threads_started[match(name, metadata$Author)], "<br>",
      "Influence: ", metadata$influence[match(name, metadata$Author)], " (based on the number of connections)", "<br><br>",
      "<strong>Comments per Newsgroup</strong><br>",
      comments_per_newsgroup,
      "</div>"  # End of custom tooltip styling
    )
  )

# Identify current min and max sizes for nodes
current_min <- min(nodes$size, na.rm = TRUE)
current_max <- max(nodes$size, na.rm = TRUE)

# Define new desired range for node sizes
new_min <- 15  # Minimum size
new_max <- 30  # Maximum size

# Apply Min-Max scaling to the 'size' column
nodes <- nodes %>%
  mutate(
    size = ((size - current_min) / (current_max - current_min)) * (new_max - new_min) + new_min
  )

nodes
edges
summary(nodes)
summary(edges)
```

```{r Visualize the Graph}
# Libraries
library(dplyr)
library(tidyr)
library(visNetwork)
library(igraph)  # Needed for community detection
library(RColorBrewer)  # For generating pastel colors

# Convert node names to zero-based indices
nodes <- nodes %>%
  mutate(id = 0:(n() - 1))  # Create a new 'id' column for nodes

# Convert 'source' and 'target' in edges to indices using the 'name' to 'id' mapping
edges <- edges %>%
  mutate(
    from = match(source, nodes$name) - 1,  # Zero-based index
    to = match(target, nodes$name) - 1     # Zero-based index
  )

# Automatically assign colors to communities using RColorBrewer
num_communities <- length(unique(node_communities$community))
colors <- brewer.pal(min(num_communities, 9), "Set1")  # Use Set1 palette for distinct colors

# If you have more than 9 communities and need more colors, you can create a larger palette
# by repeating or expanding the Set1 palette
if (num_communities > 9) {
  colors <- colorRampPalette(brewer.pal(9, "Set1"))(num_communities)
}
# Merge nodes with their community data and assign colors automatically
nodes <- nodes %>%
  mutate(color = colors[community])

# Create a network visualization with a force-directed layout
network_graph <- visNetwork(nodes, edges, width = "100vw", height = "100vh") %>%
  visNodes(
    size = nodes$size * 5,
    font = list(size = 15),
    color = list(
      border = "black",
      highlight = "red"
    ),
    title = nodes$title  # Use the title for hover popups
  ) %>%
  visEdges(
    width = ~weight,
    color = list(color = 'gray', highlight = 'red'),
    smooth = list(enabled = TRUE, type = "dynamic", roundness = 0.5)  # Enable smooth dynamic edges with medium roundness
  ) %>%
  visOptions(
    highlightNearest = list(enabled = TRUE, hover = TRUE),
    nodesIdSelection = list(enabled = TRUE)
  ) %>%
  visPhysics(
    stabilization = TRUE,
    solver = "barnesHut",
    barnesHut = list(gravitationalConstant = -8000, springLength = 100, springConstant = 0.01)
  ) %>%
  visInteraction(
    dragNodes = TRUE,
    dragView = TRUE,
    zoomView = TRUE
  ) %>%
  visLayout(
    improvedLayout = TRUE
  )

# Display the network graph in the RStudio Viewer
network_graph

# Save the network graph to an HTML file with full width and height
network_graph_path <- file.path(output_directory, "images and tables/network_graph.html")
visSave(network_graph, file = network_graph_path)

# Step 4: Add the custom legend directly into the HTML file after it is saved
html_legend <- '
<div style="position: absolute; bottom: 20px; right: 20px; background-color: white; border: 1px solid #666; padding: 10px; border-radius: 5px; font-family: Arial, sans-serif;">
  <div style="margin-bottom: 5px;"><strong>Color</strong> = Community (Louvain)</div>
  <div><strong>Node Size</strong> = Influence</div>
</div>
'

# Inject the legend into the HTML file
html_content <- readLines(network_graph_path)
html_content <- c(html_content, html_legend)
writeLines(html_content, network_graph_path)
```

>>>>

---
title: "Paper Visualization"
author: "Emerson Johnston"
lastmodifeddate: "2024-09-01"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

@@

# Load the datasets
all_threads <- read.csv(file.path(threads_directory, "aids_related_threads_82TO86.csv"))
all_comments <- read.csv(file.path(comments_directory, "aids_related_comments_82TO86.csv"))
```

```{r R CSV Cleaning}
all_threads <- all_threads %>% drop_na()
all_comments <- all_comments %>% drop_na()
all_comments$Date <- as.Date(all_comments$Date, format = "%Y-%m-%d")
all_threads$Date <- as.Date(all_threads$Date, format = "%Y-%m-%d")
```

@@

# Load the datasets with the correct file paths
all_threads = pd.read_csv(os.path.join(threads_directory, "aids_related_threads_82TO86.csv"))
all_comments = pd.read_csv(os.path.join(comments_directory, "aids_related_comments_82TO86.csv"))
```

# Theme Prevelance Hypothesis

# Emotional Tone Hypothesis

# Author Impact Hypothesis

### 2024-09-01 Scripts - Data Cleaning and Visuals/_CSV Cleaning.Rmd
testing

@@

# Save the comments dataframe to CSV
write.csv(comments_in_keyword_threads, file.path(comments_directory, "aids_related_comments.csv"), row.names = FALSE)

@@

# Save the threads dataframe to CSV
write.csv(threads_summary_df, file.path(threads_directory, "aids_related_threads.csv"), row.names = FALSE)
```

>>>>

Filtering to 1982-1986
```{r Filtering to 1982-1986}
all_comments <- all_comments %>%
  filter(Date < as.Date("1987-01-01")) %>% filter(Date > as.Date("1982-01-01"))

all_threads <- all_threads %>%
  filter(Date < as.Date("1987-01-01")) %>% filter(Date > as.Date("1982-01-01"))

write.csv(all_threads, file.path(threads_directory, "combined_threads_cleaned_82TO86.csv"), row.names = FALSE)
write.csv(all_comments, file.path(comments_directory, "combined_comments_cleaned_82TO86.csv"), row.names = FALSE)
```

@@

# Save the comments dataframe to CSV
write.csv(comments_in_keyword_threads, file.path(comments_directory, "aids_related_comments_82TO86.csv"), row.names = FALSE)

@@

# Save the threads dataframe to CSV
write.csv(threads_summary_df, file.path(threads_directory, "aids_related_threads_82TO86.csv"), row.names = FALSE)
```
